\documentclass{article}
\usepackage{elf}


\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}} %partial derivative template
\newcommand{\pard}[2]{\partial #1 / \partial #2}
\newcommand{\spbox}[1]{ \text{ #1 }} %space box for formatting words inside an eq
\newcommand{\csp}{, \;} %comma and space

%conditional function template
\newcommand{\cfunc}[5]{
    #1 = 
    \begin{cases} 
        #2 & #3 \\
        #4 & #5
    \end{cases}
}
%conditional function template for three conditions
\newcommand{\ctfunc}[7]{
    #1 = 
    \begin{cases} 
        #2 & #3 \\
        #4 & #5 \\
        #6 & #7
    \end{cases}
}

\title{A Robust Solution to Henry's Problem}
\author{Erich L. Foster, Stephen W. Wheatcraft, Aleksey Telyakovskiy}
%Graduate Program of Hydrologic Sciences, University of Nevada, Reno

\begin{document}

\maketitle

\begin{abstract}
Henry's Semi-Analytic Solution to Seawater Intrusion has been used as a 
benchmark for numerical solutions for many years. However, its ability to use 
parameters that are more representative of narrow zones of dispersion has been 
limited. The method used by Henry to evaluate his analytic solution has been 
tempered by the limited ability to increase the number of Fourier Coefficients 
used, and this may possibly lead to the inability of those methods to solve 
Henry's Problem using parameters that would simulate narrow zones of dispersion. 
Newton's Method however, is a more robust numerical method than those previously 
used, and therefore will not limit the number of coefficients used. The robust 
nature of Newton's Method leads to the ability to use an increased number of 
Fourier coefficients, and therefore will allow for parameters that can simulate 
narrower zones of dispersion.
\end{abstract}

\input{variable.tex}

\section{Introduction}
\input{Intro.tex}

\section{Governing Equations}
\input{GoverningEQs.tex}

\section{Fourier-Galerkin Method}
\input{FourierGalerkin.tex}

\section{Newton-Raphson Formulation}
\input{Newton.tex}

\section{Application}
\input{Application.tex}

\section{Results}

\section{Conclusions}
\inpute{Conclusions.text}

  \bibliographystyle{plain}
  \bibliography{PolyClip}
\begin{thebibliography}{30}
    \bibitem{Baxter}Baxter, G. P., and C. C. Wallace (1916). Changes in Volume 
    Upon Solution in Water of the Halogen Salts of the Alkali Metals, IX. 
     \textit{Journal of American Chemical Society}, 38, 70-104.

    \bibitem{Bear}Bear, J. (1988). \textit{Dynamics of Fluids in Porous Media} 
    (Dover Ed.), Dover Pub., New York.

    \bibitem{Greenspan}Greenspan, D, and V. Casulli (1988). \textit{Numerical 
    Analysis for Applied Mathematics, Science, and Engineering.} Perseus Pub., 
    Cambridge, M.A.

    \bibitem{Henry60}Henry, H. R. (1960). \textit{Salt Intrusion into Coastal 
    Aquifers (Doctoral dissertation),} Columbia University.

    \bibitem{Henry64}Henry, H. R. (1964). Effects of Dispersion on Salt 
    Encroachment in Coastal Aquifers, in \textit{Sea Water in Coastal Aquifers},
     \textit{U.S. Geol. Surv. Water-Supply Pap.}, 1613-C, 70-C84.

    \bibitem{Hosking}Hosking, R. J., J. Joe, D. C. Joyce, and J. C. Turner 
    (1996). \textit{First Steps in Numerical Analysis} (2nd ed.).
    Arnold, London. 

    \bibitem{Pinder}Pinder, G. F., and H. H. Cooper Jr. (1970). A Numerical 
    Technique for Calculating the Transient Position of the Seawater Front, 
     \textit{Water Resour. Res.}, 6, 875-882.

    \bibitem{Press}Press, W.H., S.A. Teukolsky, W.T. Vetterling, and B.P. Flannery 
    (1992), \textit{Numerical Recipes in Fortran, The Art of Scientific Computing, 
    Second Edition}, Cambridge University Press, New York.

    \bibitem{Segol}S\'egol, G. (1994). \textit{Classical Groundwater Simulations: 
    Proving and Improving Numerical Models}, Prentice-Hall, Old Tappan, N.J. 

    \bibitem{Simpson}Simpson, M. J., and T. P. Clement (2003), 
    Theoretical Analysis of the Worthiness of the Henry and Elder Problems as 
    Benchmarks of Density-Dependent Groundwater Flow Models, \textit{Adv. Water 
    Resour.}, 26, 17-31.

    \bibitem{Voss}Voss, C. I. \& Souza W. R. (1987). Variable Density Flow and 
    Solute Transport Simulation of Regional Aquifers Containing a Narrow 
    Freshwater-Seawater Transition Zone, \textit{Water Resour. Res.}, 23, 
    1851-1866.
\end{thebibliography}

\end{document}
